### 2017-04-17 paper/oopsla17-submission/intro2.tex
colorbox borders to degrade to b/w better
hyphen

% In Robin Milner's memorable words
% %
% ``types are the leaven of computer programming;
  % they make it digestible''~\cite{tapl}.
%
Types are awesome.
%
Languages like \ocaml and \haskell make
the value-proposition for types even more
appealing by using constraints to automatically
synthesize the types for all program terms
without troubling the programmer for any
annotations.
%
Unfortunately, this automation has come at a price.
Type annotations signify
the programmer's intent and help to correctly
blame the erroneous sub-term when the code is
ill-typed.
%
In the absence of such signifiers, automatic
type inference algorithms are prone to report
type errors far from their actual source
\citep{Wand1986-nw}.
%
While this can seem like a minor annoyance to
veteran programmers, \citet{Joosten1993-yx} have found
that novices often focus their attention on the \emph{location}
reported and disregard the \emph{message}.

@@

Our \emph{third contribution} (\autoref{sec:evaluation})
is a systematic evaluation of our data-driven approach
using different classes of features like the above, and
with three different classification algorithms: logistic
regression, decision trees, and neural networks.
%
Our evaluation lets us identify the best features and
classifier and empirically characterize the importance
of different features for error localization.
%
In particular, we find that while machine learning
over syntactic features of each term in isolation
performs worse than existing
purely constraint based approaches (\eg \ocaml, \sherrloc),
augmenting the data with a single feature corresponding to
the \emph{type error slice} \citep{Tip2001-qp} brings our
classifiers up to par with the state of the art,
and further augmenting the data with \emph{contextual}
features allows our classifiers to outperform
the state of the art by \ToolnameWinSherrloc percentage points.
% In particular, we find that while machine learning
% on its own performs slightly worse than existing
% purely constraint based approaches (\eg \ocaml, \sherrloc),
% once we augment the data with feature abstraction
% corresponding to the \emph{type error slice} \citep{Tip2001-qp},
% the resulting classifier significantly outperforms the
% state of the art by 18 percentage points.

>>>>

% In Robin Milner's memorable words
% %
% ``types are the leaven of computer programming;
  % they make it digestible''~\cite{tapl}.
%
%Types are awesome.
When viewed fully, types are awe-inspiring.
%
Languages like \ocaml and \haskell make
the value-proposition for types even more
appealing by using constraints to automatically
synthesize the types for all program terms
without troubling the programmer for any
annotations.
%
Unfortunately, this automation has come at a price.
Type annotations signify
the programmer's intent and help to correctly
blame the erroneous sub-term when the code is
ill-typed.
%
In the absence of such signifiers, automatic
type inference algorithms are prone to report
type errors far from their source
\citep{Wand1986-nw}.
%
While this can seem like a minor annoyance to
veteran programmers, \citet{Joosten1993-yx} have found
that novices often focus their attention on the \emph{location}
reported and disregard the \emph{message}.

@@

Our \emph{third contribution} (\autoref{sec:evaluation})
is a systematic evaluation of our data-driven approach
using different classes of features like the above, and
with three different classification algorithms: logistic
regression, decision trees, and neural networks.
%
Our evaluation lets us identify the best features and
classifier and empirically characterize the importance
of different features for error localization.
%
In particular, we find that while machine learning
over syntactic features of each term in isolation
performs worse than existing
purely constraint-based approaches (\eg \ocaml, \sherrloc),
augmenting the data with a single feature corresponding to
the \emph{type error slice} \citep{Tip2001-qp} brings our
classifiers up to par with the state of the art,
and further augmenting the data with \emph{contextual}
features allows our classifiers to outperform
the state of the art by \ToolnameWinSherrloc percentage points.
% In particular, we find that while machine learning
% on its own performs slightly worse than existing
% purely constraint based approaches (\eg \ocaml, \sherrloc),
% once we augment the data with feature abstraction
% corresponding to the \emph{type error slice} \citep{Tip2001-qp},
% the resulting classifier significantly outperforms the
% state of the art by 18 percentage points.
